Study on the degree of transparency of the local public administration in Romania

### 2023-06-19 Article.Rmd
Articol
a

---
title             : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"
shorttitle        : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"
author: 
  - name          : "Mari-Isabella Stan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1"
    email         : "stanisabella@yahoo.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Tănase Tasențe"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, Romania, Faculty of Law and Administrative Sciences"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib", "transparenta.bib"]
floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
documentclass     : "apa7"
classoption       : "man"
output            :
  pdf_document    : papaja::apa6_pdf
  word_document   : papaja::apa6_docx
header-includes:
  - \usepackage{ragged2e}
---

```{r setup, include = FALSE}
  library(papaja); library(knitr); library(kableExtra)
  r_refs("r-references.bib")
```

@@

# Results
```{r Analysis, echo=F, include=F}
  source("01 - Analysis.R")
```
# Analiza contingenței în funcție de rangul localității 
```{r Range, echo=F}
  # Item 1
  chi.1 <- round(chi.R.I1$statistic, 2);  df.chi.1 <- chi.R.I1$parameter; p.chi.1 <- chi.R.I1$p.value
  mun.n.1 <- R.I.1.prop[1,1]; mun.y.1 <- R.I.1.prop[2,1]
  cit.n.1 <- R.I.1.prop[1,2]; cit.y.1 <- R.I.1.prop[2,2]
  vil.n.1 <- R.I.1.prop[1,3]; vil.y.1 <- R.I.1.prop[2,3]

@@

```
```{r Moz-Range-I1, fig.align='center', fig.cap='Contingency: - Locality rank vs. Normative documents'}
  knitr::include_graphics("Article_files/figure-latex/Analysis-1.png")
```
```{r Bar-Range-I1, echo = F, warning=F, fig.align='center', fig.cap='Barplot: - Locality rank vs. Normative documents'}
  R.I.1.plot
```
## *a. Actele normative care reglementează organizarea și funcționarea autorității sau instituției publice*
În privința **actelor normative care reglementează organizarea și funcționarea autorității sau instituției publice** rezultă diferențe statistic semnificative (\(\chi\)^2^(`r df.chi.1`)=`r chi.1`, p=`r p.chi.1`) determinate de rangul unității administrativ teritoriale. Într-adevăr, se pare că actele normative de acest tip nu există mai curând la nivelul **comunelor** (`r vil.n.1`% „Nu” față de `r vil.y.1`% „Da”) în comparație cu orașele (`r cit.n.1`% „Nu” față de `r cit.y.1`% „Da”) și municipiile (`r mun.n.1`% „Nu” față de `r mun.y.1`% „Da”), doar între comune și celelalte două categorii de unități administrative existând diferențe statistic semnificative (vezi figurile \@ref(fig:Moz-Range-I1) și \@ref(fig:Bar-Range-I1)).

@@

>>>>

---
title             : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"
shorttitle        : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"

author: 
  - name          : "Mari-Isabella Stan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "stanisabella@yahoo.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

  - name          : "Tănase Tasențe"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, Romania, Faculty of Law and Administrative"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
  library(papaja); library(knitr); library(kableExtra); library(png)
  r_refs("r-references.bib")
```

@@

# Results
```{r Analysis, echo=F, include=F}
  source("01 - Analysis.R")
```
# Contingency analysis based on the rank of the locality
```{r Range, echo=F}
  # Item 1
  chi.1 <- round(chi.R.I1$statistic, 2);  df.chi.1 <- chi.R.I1$parameter; p.chi.1 <- chi.R.I1$p.value
  mun.n.1 <- R.I.1.prop[1,1]; mun.y.1 <- R.I.1.prop[2,1]
  cit.n.1 <- R.I.1.prop[1,2]; cit.y.1 <- R.I.1.prop[2,2]
  vil.n.1 <- R.I.1.prop[1,3]; vil.y.1 <- R.I.1.prop[2,3]

@@

```
```{r Moz-Range-I1, fig.align='center', fig.cap='Contingency: - Locality rank vs. Normative documents'}
  knitr::include_graphics("Article_files/figure-latex/Analysis-1.png")
```
```{r Bar-Range-I1, echo = F, warning=F, fig.align='center', fig.cap='Barplot: - Locality rank vs. Normative documents'}
  R.I.1.plot
```
## *a. The normative acts regulating the organization and operation of the public authority or institution*
In terms of the normative acts regulating the organization and operation of the public authority or institution, statistically significant differences emerge (\(\chi\)^2^(`r df.chi.1`)=`r chi.1`, p=`r p.chi.1`), driven by the rank of the administrative-territorial unit. Indeed, it appears that these types of normative acts are less likely to exist at the level of villages (`r vil.n.1`%  "No" versus `r vil.y.1`% "Yes") compared to towns (`r cit.n.1`% versus `r cit.y.1`% "Yes") and municipalities (`r mun.n.1`% "No" versus `r mun.y.1`%  "Yes"), with statistically significant differences only between villages and the other two categories of administrative units (see figures \@ref(fig:Moz-Range-I1) și \@ref(fig:Bar-Range-I1)).

În privința **actelor normative care reglementează organizarea și funcționarea autorității sau instituției publice** rezultă diferențe statistic semnificative (\(\chi\)^2^(`r df.chi.1`)=`r chi.1`, p=`r p.chi.1`) determinate de rangul unității administrativ teritoriale. Într-adevăr, se pare că actele normative de acest tip nu există mai curând la nivelul **comunelor** (`r vil.n.1`% „Nu” față de `r vil.y.1`% „Da”) în comparație cu orașele (`r cit.n.1`% „Nu” față de `r cit.y.1`% „Da”) și municipiile (`r mun.n.1`% „Nu” față de `r mun.y.1`% „Da”), doar între comune și celelalte două categorii de unități administrative existând diferențe statistic semnificative (vezi figurile \@ref(fig:Moz-Range-I1) și \@ref(fig:Bar-Range-I1)).

@@

# Analiza contingenței în funcție de regiunea de dezvoltare a României
